\manualchapter{Project Plan}{Project Plan}
\chaptermark{Project Plan}
The following section describes work planned.

\section{Work plan}

\subsection{Prototype SAT solver}
The current plan is to write a naive SAT solver implementation that can perform basic clause learning. This can then be rewritten with clearer structure and modern state of the art optimizations.
The following are things that need to be achieved in the prototype.
\begin{enumerate}
\item Unit resolution using unit clauses.
\item Pure literal elimination.
\item Basic conflict analysis and clause learning
\item (Optional) two watched literal data structures
\end{enumerate}

\subsection{Industrial Strength CDCL SAT solver}
Restructure the prototype to include the following

\begin{enumerate}
\item Preprocessing. Follow the work of MiniSAT and SATELite
\item Heuristics. It would be nice to be able to plug in a variety of heuristics.
\item Efficient conflict analysis. I remember that conflict analysis can be optimized using some form of lookup table. We probably want a decent learning scheme like 1st UIP or whatever the state of the art is.
\item Proof trace. We want to be able to generate a proof trace from our solver. We could have different builds of the solver one of which is optimized i.e. it generates no trace and another with trace generation.
\item Incremental SAT solving. We want the ability to incrementally add clauses to the solver while it runs.
\item Restarts. The solver should be capable of restarting the proof search with its newly learned clauses. The heuristics will hopefully then guide the solver down a better path towards a solution.
\end{enumerate}

\subsection{Parallelized SAT solving}
The work here will involve parallelizing the above CDCL SAT in a style similar to Many-SAT. This will hopefully result in a fast powerful solver.
\begin{enumerate}
\item Data structures. We need a data structure that can share the learned clauses between solvers on the fly.
\item Multi-threading. How do we parameterize our bank of SAT solvers? What algorithms work well together? 
\item Heuristics.
\end{enumerate}

\subsection{SMT Solver}
This will be hard. I haven't really thought about it.

\subsection{C++ Model Checker/ Theorem Prover}
Blue sky thinking.

\subsection{Model Based Testing for C++}
Blue sky thinking. Use our C++ model to automatically generate unit tests and validate the model.



